Results

### 2019-08-01 analysis/03_analysis.Rmd
HMC diagnostics, starting with intercept-only

```{r load-data-output, warning=FALSE, message=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 1                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load and extract data and model output (see model-calibration.R)
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit
```

@@

@@

# # Check the effective sample size (not working for a hierarchical model?)
# check_n_eff(fit)
# 
# # Check the Rhat statistic (not working for a hierarchical model?)
# check_rhat(fit)

# Check trace plots (SUBSET?)
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    regex_pars = "Theta",
    n_warmup = 1000,
    facet_args = list(
      nrow = round((data$L * data$C)/7), 
      labeller = label_parsed
    )
  )

@@

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

>>>>

```{r load-data-output, warning=FALSE, message=FALSE}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load and extract data and model output (see model-calibration.R)
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit
```

@@

# Thetas
draws_theta <- fit %>% 
  extract(
    pars = str_c("Theta[", 1:13, ",1]"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_theta %>% 
  mcmc_hist_by_chain()

draws_theta %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# Extract the L_Omega parameters only and look at trace plots, etc.

# L_Omega
draws_L_Omega <- fit %>% 
  extract(
    regex_pars = c("L_Omega"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_theta %>% 
  mcmc_hist_by_chain()

draws_theta %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# # Check diagnostics
# check_all_diagnostics(fit)

@@

# # Check the effective sample size (NOT WORKING?)
# check_n_eff(fit)
# 
# # Check the Rhat statistic (NOT WORKING?)
# check_rhat(fit)

# Check trace plots (SUBSET?)
color_scheme_set("mix-blue-red")
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    pars = str_c("Theta[", 1:13, ",1]"),
    n_warmup = 2000,
    facet_args = list(
      nrow = 2, 
      labeller = label_parsed
    )
  )

@@

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 1000)
